{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-07-31 paper/tex/sections/variations.tex
minor changes to variations

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See Sec.~\ref{sec:detection_rate_analysis} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}. \todo{Will add R, T once Floor says that they are done}}
    \label{fig:detection_rates}
\end{figure*}

@@

If we instead use the optimistic CE scenario when setting case BB mass transfer to be unstable (model \modCaseBBOpt{}) we find that the rates instead uniformly increase across DCO types. This is both from the natural increases from using the optimistic CE scenario (see Sec.~\ref{sec:detection_rate_CE_trends} in which we discuss model \modOpt{}), as well as additional increases from adding more DCOs formed through CE events after case BB mass transfer. This explains why we see more detections for BHNSs and NSNSs in model \modCaseBBOpt{} than in model \modOpt{}.

@@

\todo{Discuss $\alpha_{\rm CE}$ changes once Floor ready}

@@

The progenitors of BHNSs tend to be less massive than those of BHBHs. Less massive stars expand less during the Hertzsprung gap and thus initiate CE events less frequently in this phase. This explains why the relative increase in model \modOpt{} compared to the fiducial model is lower for BHNSs. For the same reason, the NSNS detection rate shows little significant change.

@@

\todo{dicuss no BH kick when done}
%The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.

>>>>

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}. \todo{Will add R, T once Floor says that they are done}}
    \label{fig:detection_rates}
\end{figure*}

@@

If we instead use the optimistic CE scenario when setting case BB mass transfer to be unstable (model \modCaseBBOpt{}) we find that the rates instead uniformly increase across DCO types. This is both from the natural increases from using the optimistic CE scenario (see discussion of model \modOpt{} in Sec.~\ref{sec:detection_rate_CE_trends}), as well as additional increases from adding more DCOs formed through CE events after case BB mass transfer. This explains why we see more detections for BHNSs and NSNSs in model \modCaseBBOpt{} than in model \modOpt{}.

@@

\todo{Discuss $\alpha_{\rm CE}$ changes once I understand them (:}

@@

The progenitors of BHNSs tend to be less massive than those of BHBHs. Less massive stars expand less during the Hertzsprung gap and thus initiate CE events less frequently in this phase. For these reasons, as can be seen most clearly in Fig.~\ref{fig:dco_relative_rates}, the relative increase in model \modOpt{} compared to the fiducial model is lower than BHBHs for BHNSs. For the same reason, the NSNS detection rate shows little significant change.

@@

\todo{ensure this noBHkick description still applies} In model \modNoBH{} we do not give black holes natal kicks. Rate is higher than fiducial for BHBH and BHNS but slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick. NSNSs are unaffected as one would assume.
